Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint

### 2014-11-14 approach.tex
teaser fig caption

\begin{figure}[t]
  \begin{center}
  \begin{tabular}{cc}
     \includegraphics[width=0.5\linewidth]{whotime} & 
     \includegraphics[width=0.5\linewidth]{speedup}\\
     (a) & (b) \\
 \end{tabular}
  \end{center}
  \caption{(a) Realtime analysis of whitening. HOG means feature extraction time, WHO-Chol uses method of \cite{Hariharan12} and WHO-CG uses iterative Conjugate Gradient, and NZ-WHO-CG uses only non-zero cells and use Conjugate Gradient. (b) final speed of using NZ-WHO compare to WHO}
  \label{fig:whotime}
\end{figure}
%
\begin{figure}[t]
  \centering
  \includegraphics[width=0.5\linewidth]{residual}
  \caption{Residuals from different method}
  \label{fig:whoresidual}
\end{figure}

>>>>

\begin{figure}[t]
  \begin{center}
  \begin{tabular}{cc}
     \includegraphics[width=0.5\linewidth]{whotime} & 
     \includegraphics[width=0.5\linewidth]{speedup}\\
     (a) & (b) \\
 \end{tabular}
  \end{center}
  \caption{(a) Runtime analysis of whitening. HOG means feature
    extraction time, WHO-Chol uses ~\cite{Hariharan12} and
    WHO-CG uses iterative Conjugate Gradient. NZ-WHO-CG uses only
    non-zero cells and Conjugate Gradient. (b) final speedup
    of NZ-WHO vs. WHO.}
  \label{fig:whotime}
\end{figure}
%
\begin{figure}[t]
  \centering
  \includegraphics[width=0.5\linewidth]{residual}
  \caption{Residuals from different method}
  \label{fig:whoresidual}
\end{figure}
